ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-26 pyked.tex
draft future work
a bit more in conclusions

% (Provide 2-4 keywords describing your research. Only abbreviations firmly
% established in the field may be used. These keywords will be used for
% sessioning/indexing purposes.)
\begin{keyword}
    chemical kinetics\sep software\sep database
\end{keyword}

@@

>>>>

% (Provide 2-4 keywords describing your research. Only abbreviations firmly
% established in the field may be used. These keywords will be used for
% sessioning/indexing purposes.)
\begin{keyword}
    chemical kinetics\sep data standard\sep software\sep database
\end{keyword}

@@

In this article, we introduced the \ck{} data format for describing measurements
taken from fundamental combustion experiments, as well as the Python-based tool
\pk{} for working with the format. Currently, \ck{} supports ignition delay data
from studies using shock tubes and rapid compression machines.

We are currently incorporating support for specifying uncertainty in all quantities.
Version 1.0 of \ck{}\slash \pk{} will include ...
Later versions will support measurements from additional fundamental experiments,
including laminar flames and flow reactors.
